\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}
\RequirePackage{fontawesome}
\usepackage{tikz}
\usetikzlibrary{svg.path}


\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

\begin{document}

%----------HEADER-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  {\LARGE \textbf{John Doe}} & \href{mailto:john.doe@email.com}{john.doe@email.com} \\
  Web Developer & (123) 456-7890 \\
  \href{https://www.linkedin.com/in/johndoe}{linkedin.com/in/johndoe} | \href{https://github.com/johndoe}{github.com/johndoe} & City, State
\end{tabular*}

%--------SUMMARY------------------
\section*{\textcolor{heading}{Summary}}
\noindent
Highly motivated and skilled Web Developer with 5+ years of experience in designing and developing responsive and user-friendly web applications. Proficient in front-end and back-end technologies, with a strong focus on delivering high-quality code and exceptional user experiences.

%--------SKILLS------------------
\section*{\textcolor{heading}{Skills}}
\noindent
\textbf{Front-end:} HTML5, CSS3, JavaScript (ES6+), React, Angular, Vue.js, Responsive Design, UI/UX Design\\
\textbf{Back-end:} Node.js, Python (Django, Flask), SQL, NoSQL (MongoDB), RESTful APIs\\
\textbf{Tools:} Git, Docker, Webpack, Babel, VS Code, Jira

%--------EXPERIENCE------------------
\section*{\textcolor{heading}{Experience}}
\noindent
\textbf{Senior Web Developer} | ABC Company | 2020 - Present \\
\begin{itemize}[leftmargin=0.2in, itemsep=0pt]
    \item Developed and maintained responsive web applications using React and Node.js.
    \item Collaborated with cross-functional teams to deliver high-quality software solutions.
    \item Optimized website performance and improved user experience, resulting in a 20\% increase in user engagement.
    \item Implemented RESTful APIs for seamless integration with back-end systems.
\end{itemize}

\noindent
\textbf{Web Developer} | XYZ Corporation | 2018 - 2020 \\
\begin{itemize}[leftmargin=0.2in, itemsep=0pt]
    \item Designed and developed web pages using HTML, CSS, and JavaScript.
    \item Assisted in the development of a large-scale e-commerce platform.
    \item Resolved website bugs and improved website functionality.
\end{itemize}

%--------EDUCATION------------------
\section*{\textcolor{heading}{Education}}
\noindent
\textbf{Bachelor of Science in Computer Science} | University of Example | 2014 - 2018

%--------PROJECTS------------------
\section*{\textcolor{heading}{Projects}}
\noindent
\textbf{E-commerce Website} | GitHub: \href{https://github.com/johndoe/ecommerce}{github.com/johndoe/ecommerce} \\
Developed a fully functional e-commerce website using React and Node.js, featuring user authentication, product management, and payment integration.

\noindent
\textbf{Portfolio Website} | \href{https://johndoe-portfolio.com}{johndoe-portfolio.com} \\
Created a personal portfolio website to showcase web development skills and projects, using Vue.js and responsive design principles.

\end{document}